\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2021-11-15 manuscript.Rmd
scale curve is moved

```{r setup, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=600)
options(knitr.duplicate.label = "allow")
set.seed(123)
par(family = "Arial")
```

@@

library(papaja) # devtools::install_github("crsh/papaja")
library(lavaan)
library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
library(semTools)
library(MOTE)
library(car)#revercoding 
library(psych)
library(dlookr)
library(plyr)
library(tidyverse)
library(qgraph)
library(kableExtra)
library(paran) # Parallel analysis
library(EFA.MRFA) # Hull method
library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
library(DiagrammeRsvg) #For DiagrammeR
library(rsvg) #For DiagrammeR
library(ggcorrplot)
library(semTable)
library(magick)
library(mirt)
library(gtsummary)
library(gt)
library(gtExtras)
library(likert)
library(VIM) #Missing data
library(kutils)
library(simsem)
library(tabledown)
library(readxl)
r_refs("references.bib")
```

@@

## Semantic Analysis 
To find out if our developed tool is overlapping with existing instruments, we subjected the items of LEBA to the "Semantic Scale Network"(SSN) analysis[@rosenbusch2020semantic]. The SSN detects semantically related scales and provides cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic]. Pair of scales with a cosine similarity index value of 1 indicates they are perfectly semantically similar scales indicating redundancy. LEBA  appeared most strongly related to scales about sleep: "Sleep Disturbance Scale For Children" [@bruni1996sleep] and "WHO-Composite International Diagnostic Interview (CIDI): Insomnia"[@who1990].The cosine similarities lie between .47 to .51. Two factors of our LEBA tool: "Using phone and smart-watch in bed" and "Using light before bedtime" dealt with light exposure related behavior pertaining to sleep quality. As such the similarity index obtained is expected.

@@

Table \@ref(tab:itemfittab) summarizes the item fit indexes of the items. All the items fitted well to the respective models as assessed by  RMSEA value obtained from Signed-$\chi^2$ index implementation. All of the items had RMSEA value $\le$.06 indicating adequate fit. Figure \@ref(fig:personfit) depicts the person fit of out fitted models. Person fit indicates the validity and meaningfulness of the fitted model at the participants latent trait level [@desjardinsHandbookEducationalMeasurement2018]. We estimated the person fit statistics using standardized fit index Zh statistics [@drasgow1985appropriateness]. Zh < -2 should be considered as a misfit. Fig indicates that Zh is larger than -2 for most participants, suggesting a good fit of the selected IRT models.
```{r itemfittab, results='asis',warning=F, message=F}
apa_table(itemfit, caption ="Item fit statistics for the fitted models")
```

@@

Next, we generated scale characteristics curve (Figure \@ref(fig:scalechar)) which plotted estimated theta score against the expected true score. The purpose of this scale characteristics curve is to find the corresponding expected true score for the given estimated theta score.

```{r scalechar, fig.cap="Scale characteristic curve of the five fitted IRT models (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, out.width="100%", out.height="120%"}

>>>>

```{r setup, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=1200)
options(knitr.duplicate.label = "allow")
set.seed(123)
par(family = "Arial")
```

@@

library(papaja) # devtools::install_github("crsh/papaja")
library(lavaan)
library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
library(semTools)
library(MOTE)
library(car)#reversecoding 
library(psych)
library(dlookr)
library(plyr)
library(tidyverse)
library(qgraph)
library(kableExtra)
library(paran) # Parallel analysis
library(EFA.MRFA) # Hull method
library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
library(DiagrammeRsvg) #For DiagrammeR
library(rsvg) #For DiagrammeR
library(ggcorrplot)
library(semTable)
library(magick)
library(mirt)
library(gtsummary)
library(gt)
library(gtExtras)
library(likert)
library(VIM) #Missing data
library(kutils)
library(simsem)
library(tabledown)
library(readxl)
r_refs("references.bib")
```

@@

## Semantic Analysis 
To find out if our developed tool is overlapping with existing instruments, we subjected the items of LEBA to the "Semantic Scale Network"(SSN) analysis [@rosenbusch2020semantic]. The SSN detects semantically related scales and provides cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic]. Pair of scales with a cosine similarity index value of 1 indicates they are perfectly semantically similar scales indicating redundancy. LEBA  appeared most strongly related to scales about sleep: "Sleep Disturbance Scale For Children" [@bruni1996sleep] and "WHO-Composite International Diagnostic Interview (CIDI): Insomnia"[@who1990].The cosine similarities lie between .47 to .51. Two factors of our LEBA tool: "Using phone and smart-watch in bed" and "Using light before bedtime" dealt with light exposure related behavior pertaining to sleep quality. As such the similarity index obtained is expected.

@@

Table \@ref(tab:itemfittab) summarizes the item fit indexes of the items. All the items fitted well to the respective models as assessed by  RMSEA value obtained from Signed-$\chi^2$ index implementation. All of the items had RMSEA value $\le$.06 indicating adequate fit. Figure \@ref(fig:personfit) depicts the person fit of out fitted models. Person fit indicates the validity and meaningfulness of the fitted model at the participants latent trait level [@desjardinsHandbookEducationalMeasurement2018]. We estimated the person fit statistics using standardized fit index Zh statistics [@drasgow1985appropriateness]. Zh < -2 should be considered as a misfit. Fig indicates that Zh is larger than -2 for most participants, suggesting a good fit of the selected IRT models.

```{r itemfittab, results='asis',warning=F, message=F}
apa_table(itemfit, caption ="Item fit statistics for the fitted models")
```

@@

```{r scalechar, eval=FALSE, fig.cap="Scale characteristic curve of the five fitted IRT models (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, include=FALSE, out.height="120%", out.width="100%"}

#Finally we generated scale characteristics curve (Figure \@ref(fig:scalechar)) which plotted estimated theta score against the expected true score. The purpose of this scale characteristics curve is to find the corresponding expected true score for the given estimated theta score of the participants.
